---
title: 'Weekly Exercises #6'
author: "Anthony Palma"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for data cleaning and plotting
library(gardenR)       # for Lisa's garden data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
theme_set(theme_minimal())
```

```{r data}
# Lisa's garden data
data("garden_harvest")

#COVID-19 data from the New York Times
covid19 <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

```



## Your first `shiny` app 

  1. This app will also use the COVID data. Make sure you load that data and all the libraries you need in the `app.R` file you create. Below, you will post a link to the app that you publish on shinyapps.io. You will create an app to compare states' cumulative number of COVID cases over time. The x-axis will be number of days since 20+ cases and the y-axis will be cumulative cases on the log scale (`scale_y_log10()`). You will have an input box where the user can choose which states to compare (`selectInput()`) and have a submit button to click once the user has chosen all states they're interested in comparing. The graph should display a different line for each state, with labels either on the graph or in a legend. Color can be used if needed. 
  
  
[My COVID Shiny App](https://ajp28117.shinyapps.io/my_shiny_app/)
  

## Warm-up exercises from tutorial

  2. Read in the fake garden harvest data. Find the data [here](https://github.com/llendway/scraping_etc/blob/main/2020_harvest.csv) and click on the `Raw` button to get a direct link to the data. 
  
```{r}
fake_harvest <- read_csv("https://raw.githubusercontent.com/llendway/scraping_etc/main/2020_harvest.csv", 
    col_types = cols(`This is my awesome data!` = col_skip(), 
        X1 = col_skip(), weight = col_number()), 
    na = "MISSING", skip = 2)%>% 
  mutate(date = mdy(date))

```
  
  
  3. Read in this [data](https://www.kaggle.com/heeraldedhia/groceries-dataset) from the kaggle website. You will need to download the data first. Save it to your project/repo folder. Do some quick checks of the data to assure it has been read in appropriately.
  
  
  

# 4 skipped (not graded)


  5. Create a table using `gt` with data from your project or from the `garden_harvest` data if your project data aren't ready.
  
```{r}
garden_table <- garden_harvest %>%
  mutate(newveg = str_to_title(vegetable)) %>% 
  gt(
  rowname_col = "date",
  groupname_col = "newveg"
) %>% 
  fmt_date(columns = vars(date),
           date_style = 1) %>% 
  cols_hide(columns = vars(units)) %>% 
  tab_footnote(
    footnote = "Weight in grams",
    locations = cells_column_labels(
      columns = vars(weight)
    )
  ) %>% 
  tab_header(title = "Garden Harvest Data") %>% 
  tab_options(column_labels.background.color = "blue",
              )
  
garden_table

```
  
  

  6. Use `patchwork` operators and functions to combine at least two graphs using your project data or `garden_harvest` data if your project data aren't read.
  

```{r}
plot_1 <-garden_harvest %>% 
  mutate(newvariety = str_to_title(variety)) %>%
  mutate(newveg = str_to_title(vegetable)) %>%
  mutate(wt_lbs = 0.00220462*weight) %>% 
  filter(newveg %in% c("Beans",
                       "Corn",
                       "Pumpkins",
                       "Squash",
                       "Tomatoes")) %>% 
  group_by(newveg, date) %>%
  summarise(daily_harvest = sum(wt_lbs)) %>% 
  mutate(cum_harvest = cumsum(daily_harvest)) %>% 
  ggplot(aes(y = cum_harvest,
             x = date,
             color = newveg)) +
  geom_line() +
  labs(title = "Vegetable Harvest Over Time",
       x ="",
       y= "Cumulative Weight in lbs",
       color = "") 

plot_2 <- garden_harvest %>%
  mutate(newvariety = str_to_title(variety)) %>% 
  filter(vegetable %in% c("pumpkins")) %>% 
  ggplot(aes(y=fct_rev(fct_infreq(newvariety)))) +
  geom_bar(fill = "purple") +
  labs(title = "Pump. Harvest by Variety",
       x = "Number of Harvests",
       y= "") 

plot_1 | plot_2

```




**DID YOU REMEMBER TO UNCOMMENT THE OPTIONS AT THE TOP?**
